Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-05-22 manuscript.Rmd
Switching to Vim editing.

```{r pagePlot, eval=TRUE, cache=FALSE}
pages.tmp <- full.df %>% filter(attributes == "pages")
years.tmp <- full.df %>% filter(attributes == "pubYear")
pages.df <- left_join(pages.tmp, years.tmp, by = "articleID") %>% 
    select(record.y, record.x) %>%
    rename(years = record.y, pages = record.x) %>%
    mutate(pages = as.numeric(pages), years = as.numeric(years)) %>%
    group_by(years) %>%
    summarise(
        Median = median(pages, na.rm=TRUE), 
        Mean.Pages = mean(pages, na.rm=TRUE),
        Std.Pages = sd(pages, na.rm=TRUE))
cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )

pages.df.melted <- reshape2::melt(pages.df, id.vars = c("years", "Std.Pages"))
pages.df2.melted <- filter(pages.df.melted, variable == "Mean.Pages")

@@

stacked.df <- as.data.frame(xtabs(N~year+studyType, evidence.summary))
stacked.df$year

@@

df <- evidence.summary2
```

```{r plotProportions, cache=FALSE}
evidence.plot <- ggplot(na.omit(df), aes(year, studyProp, colour = studyType, 
    group = studyType), na.rm=TRUE) + 
    geom_smooth(aes(fill=studyType), alpha = .40, colour = "dimgray") + facet_wrap(~studyType) + 
    theme_bw() +
    scale_fill_manual(values = cp) +   
    scale_color_manual(values = cp) + 
    theme(legend.position = "none") + 
    ylab("Proportion") + 
    geom_point(colour = "black", alpha = .60) + 
    annotate("segment", x = 1989, y = 0, xend = 2013, yend = 0, alpha = .6, 
        linetype= "solid") +
    annotate("segment", x = 1989, y = 0, xend = 1989, yend = .0175, alpha = .6, 
        linetype = "solid") +
    annotate("segment", x = 2013, y = 0, xend = 2013, yend = .0175, alpha = .6,
             linetype = "solid") +
    scale_x_continuous(breaks = seq(1989, 2014, 4)) + 
     theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
    scale_y_continuous(breaks = seq(0, .03, .005)) 
```

```{r plotClevelandAbsolute}

evidence.summary3 <- select(evidence.df, -abstract) %>% 
    group_by(journal, studyType) %>%
    summarize(N = n())

@@

```{r plotClevelandRelative}
evidence.journals <- full_join(evidence.summary3, evidence.summaryOverall, by = "journal") %>%
    group_by(journal) %>%
    mutate(Overall.N.Strength = sum(N)) %>%
    select(-studyType, N) %>%
    distinct(journal, Overall.N, Overall.N.Strength) %>%
    mutate(Prop = Overall.N.Strength / Overall.N)

@@

The length of the articles showed some change over time, going from approximately `r round(pages.df$Mean.Pages[pages.df$years == "1989"])` pages in 1989.  The length of the articles increased to about 15 pages and has remain at approximately this length since the early 2000's.  The standard deviation has remained fairly stable over the time period, ranging from `r options(digits=2); min(pages.df$Std.Pages)` to `r options(digits=2); max(pages.df$Std.Pages)`.

>>>>

```{r pagePlot, eval=TRUE, cache=FALSE}
cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )
pages.tmp <- full.df %>% filter(attributes == "pages")
years.tmp <- full.df %>% filter(attributes == "pubYear")
pages.df <- left_join(pages.tmp, years.tmp, by = "articleID") %>% 
    select(record.y, record.x) %>%
    rename(years = record.y, pages = record.x) %>%
    mutate(pages = as.numeric(pages), years = as.numeric(years)) %>%
    group_by(years) %>%
    summarise(
        Median = median(pages, na.rm=TRUE), 
        Average = mean(pages, na.rm=TRUE),
        Std.Pages = sd(pages, na.rm=TRUE))

pages.df$years <- c(1989:2013)

pages.df.melted <- reshape2::melt(pages.df, id.vars = c("years", "Std.Pages"))

pages.df2.melted <- filter(pages.df.melted, variable == "Average")

@@

stacked.df <- as.data.frame(xtabs(N~year+studyType, evidence.summary))

@@

```{r plotProportions, cache=FALSE}
df <- evidence.summary2

evidence.plot <- ggplot(na.omit(df), aes(year, studyProp, colour = studyType, 
    group = studyType), na.rm=TRUE) + 
    geom_smooth(aes(fill=studyType), alpha = .40, colour = "dimgray") + facet_wrap(~studyType) + 
    theme_bw() +
    scale_fill_manual(values = cp) +   
    scale_color_manual(values = cp) + 
    theme(legend.position = "none") + 
    ylab("Proportion") + 
    geom_point(colour = "black", alpha = .60) + 
    annotate("segment", x = 1989, y = 0, xend = 2013, yend = 0, alpha = .6, 
        linetype= "solid") +
    annotate("segment", x = 1989, y = 0, xend = 1989, yend = .0175, alpha = .6, 
        linetype = "solid") +
    annotate("segment", x = 2013, y = 0, xend = 2013, yend = .0175, alpha = .6,
             linetype = "solid") +
    scale_x_continuous(breaks = seq(1989, 2014, 4)) + 
     theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
    scale_y_continuous(breaks = seq(0, .03, .005)) 
```

```{r plotClevelandAbsolute}
evidence.summary3 <- select(evidence.df, -abstract) %>% 
    group_by(journal, studyType) %>%
    summarize(N = n())

@@

```{r plotClevelandRelative}

target.journals <- df1.reduced 
target.journals$journal <- gsub("\\s+\\d+", "", target.journals$journal)
EBP.df <- left_join(target.journals, evidence.journals, by = c("journal", "studyType")) %>%
    group_by(journal) %>%
    slice(1) %>%
    ungroup %>%
    mutate(Proportion = N.sort/Overall.N) %>%
    rename(Absolute = N.sort)

EBP.df  <- within(EBP.df, quartile <- as.integer(cut(Overall.N, quantile(Overall.N, probs=0:4/4, na.rm=TRUE), include.lowest=TRUE)))

ggplot(EBP.df, aes(Proportion, journal, size = Overall.N, colour=as.factor(quartile))) + 
    theme_bw() + 
    geom_point()

View(df1.reduced)

evidence.journals <- full_join(evidence.summary3, evidence.summaryOverall, by = "journal") %>%
    group_by(journal) %>%
    mutate(Overall.N.Strength = sum(N)) %>%
    select(-studyType, N) %>%
    distinct(journal, Overall.N, Overall.N.Strength) %>%
    mutate(Prop = Overall.N.Strength / Overall.N)

@@
